%-------------------------
% Resume in Latex
% Author : Damian D'monte
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.8in}
\addtolength{\evensidemargin}{-0.8in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.8in}
\addtolength{\textheight}{1.9in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubProjheading}[5]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      {\small#5} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Damian D'monte} \\ \vspace{4pt}
    \small 506-897-2169 $|$ \href{mailto:x@x.com}{\underline{damiandmonte@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/ddmonte}} $|$
    \href{https://github.com/...}{\underline{github.com/damiandmonte}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of New Brunswick}{Fredericton, NB}
      {Master of Computer Science}{Sep. 2019 -- Aug 2021}
    \resumeSubheading
      {Fr. Concceicao Rodrigues College of Engineering, Univeristy of Mumbai}{Mumbai, MH}
      {Bachelor of Engineering (Computer Engineering) }{May. 2013 -- May 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubProjheading
      {Graduate Research Assistant }{Sep 2019 -- Present}
      {UNB/IBM Center of Advance Studies --- Atlantic $|$ Project --- \href{https://www-01.ibm.com/ibm/cas/canada/projects?projectId=1036}{\underline{OMR in Resource Constrained Env.}} }{Fredericton, NB}
      {Technology hands-on --- C++, Gitlab CI/CD, VSCode, Docker, GDB, Linux}
      \resumeItemListStart
        \resumeItem{Researched into shared cache and ELF-based compiled code storage mechanisms for Eclipse OMR compiler technology}
        \resumeItem{Co-authored and contributed shared cache code to the open source Eclipse OMR code base.}
        \resumeItem{Developed a ELF-based shared object generator in C++ for storing WebAssembly Ahead-of-time compiled code.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubProjheading
      {Software Developer}{Jan. 2017 -- Aug. 2019}
      {Tata Consultancy Servies Limited $|$ Project --- TCS BaNCS Securites Trading - Front Office }{Mumbai, MH} 
      {Technology hands-on --- Pro*C, C++, Putty, SVN, GDB, Linux, Bash Scripting, PL/SQL Dev., SCRUM}
      \resumeItemListStart
    %%  \resumeItem{\textbf{Project}: TCS BaNCS Securites Trading, \textbf{Team}: Order Routing System (ORS/OMS) - Front Office}
      \resumeItem{Developed enhancements and resolved multiple defects/bugs impacting over a million customers for premier institutional and retail clients: \textbf{BNP Paribas, Investec, Nomura, HSBC, HDFC Securities \& Axis Securities}}
      \resumeItem{Successfully deployed TCS BaNCS Securities Trading (FNO) on UAT/SIT/Production application server's at BNP Paribas, supported UAT/Fidessa testing, provided immediate fixes, and transitioned the product to LIVE}       
      %%\resumeItem{Continuous liaison with client teams for understanding, replicating and resolving SIT, UAT and production issues}   
      \resumeItem{Implemented bash scripts to automate application startup, sanity checks, logs backup, market open and close, etc.}
      \resumeItem{Worked with cross-functional teams to ensure fulfillment of product requirements, evaluated product performance and transitioned patches from development to commercialization.}  
      \resumeItem{Acted as a customer liaison on technical issues related to product integration and deployment}
      \resumeItem{Provided production support (onsite/off-site) to institutional and retail trading desks during critical market hours.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Academic Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Mark \& Sweep Garbage Collector} $|$ \emph{C++, Git, Cmake}}{Aug 2019 -- Dec 2019}
          \resumeItemListStart
            \resumeItem{Implemented a heap management system to simulate object allocation via input trace files}
            \resumeItem{Developed Mark and Sweep garbage collector prototype to perform mark/sweep operations on heap objects}
            \resumeItem{Detected and deleted 99\% of dead objects and displayed CLI statistics post garbage collection}
          \resumeItemListEnd  
    \resumeProjectHeading
          {\textbf{DaskDB Cost Based Optimizer} $|$ \emph{Python, Pandas, DaskDB}}{Jan 2020 -- Apr 2020}
          \resumeItemListStart
            \resumeItem{Researched into cost based optimzers and created a prototype for a DaskDB data science system}
            \resumeItem{Developed a statsGather utility using Python and Pandas to gather different types of database statistics}
            \resumeItem{Implemented the functionality to generate physical plans from a logical plan and calcuated the cost of each plan.}
            %\resumeItem{Performed evaluation using the TPC-H benchmark.}
          \resumeItemListEnd
    %  \resumeProjectHeading
     %     {\textbf{NominalGDP Predictor} $|$ \emph{R, ggplot, Tidyverse, Git}}{June 2020 -- Present}
      %    \resumeItemListStart
       %     \resumeItem{Assembled a dataset of major economic indicators from multiple online sources.}
        %    \resumeItem{Performed exploratory data analysis on the dataset and trained it using linear regression and random forest model.}
         %   \resumeItem{Predicted the Nominal GDP with 95\%+ accuracy.}
          %\resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Malware Detector} $|$ \emph{Java, Maven, TravisCI, Git}}{Aug 2015 -- May 2016}
          \resumeItemListStart
            \resumeItem{Performed binary analsis on PE-executables and applied a n-gram based approach to finalize a binary feature set.}
            \resumeItem{Applied SVM classification for modelling, which in turn detected all the malicious and benign exe's.}
            \resumeItem{Designed and developed a GUI using JApplets/JSwing to automate the training, validation and prediction.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{ --- C/C++, Pro*C, Java, Racket, Python, R, \LaTeX{}, WebAssembly, JavaScript, HTML/CSS, SQL} \\
     %%\textbf{Web Technologies}{:,} \\
     %%\textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{ --- Git, Docker, GitLab CI/CD, VSCode, CMake, GDB, Putty, Eclipse, PL/SQL Developer, R Studio} \\
     %%\textbf{Libraries}{: pandas, NumPy, Matplotlib}
     \textbf{Methodologies}{ --- OOPS, UML, SDLC - Incremental Model, Agile Model - SCRUM and Extreme Programming.}
    }}
 \end{itemize}

%
%-----------PROGRAMMING SKILLS-----------
\section{Awards \& Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \resumeItemListStart
       \resumeItem{Research fellowship grant of 22,500 CAD/yr by IBM CAS-Atlantic on the Eclipse OMR project, 2019-2021. } \\
     %%\textbf{Web Technologies}{:,} \\
     %%\textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
       \resumeItem{Awarded "Star of the Month" twice for oustanding performance at TCS, Nov 2017 and Jan 2018.} \\
       \resumeItem{"Star Team Award" award at TCS for assuring a succesful direct connectivity GO-LIVE for all clients, Jun 2019.} \\
       \resumeItem{Elected as the Secretary of UNB Computer Science Graduate Students Association, Nov 2020 - present.} \\
       \resumeItemListEnd
     %%\textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}



%
%-----------PROGRAMMING SKILLS-----------
\section{Publications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \href{https://dl.acm.org/doi/abs/10.5555/3432601.3432624}{\underline{{An ELF-based storage option for the eclipse OMR ahead-of-time compiler.}}}{ In Proceedings of the 30th Annual International Conference on Computer Science and Software Engineering (CASCON '20). IBM Corp., USA, 173–178.} 
     }}
 \end{itemize}


%-------------------------------------------
\end{document}